### 2020-03-31 reviews/SIGBOVIK_2020_review_15.tex
reviews: Reformat new Mary reviews

%%%% Edit the following three lines.
%% To ensure the integrity of the triple-blind review
%% process, the contents of the \author field should not
%% reveal your identity.
\author{Exponentiator}
\rating{Better and better every day, by leaps and bounds and\\\qquad\quad\; leaping leaps and bounding bounds}
\confidence{Those guys have faith, why shouldn't I?}

%%%% The Proceedings Chair will fill in the following
%%%% two fields.
\papernum{36}
\papertitle{A thorough investigation of the degree to which the COVID-19 pandemic has enabled subpar-quality papers to make it into the proceedings of SIGBOVIK, by reducing the supply of authors willing to invest the necessary effort to produce high-quality papers}

@@

%%% Replace the following text with your review.
\vspace{-0.75in}
\center\includegraphics[height=4.25in]{walk-to-sky-exp}

>>>>

%%%% Edit the following three lines.
%% To ensure the integrity of the triple-blind review
%% process, the contents of the \author field should not
%% reveal your identity.
\author{Count Dracula, Sesame St, Cyberspace}
\rating{Great execution of absurd idea.}
\confidence{Based on counting irrelevant but objective things like vowel\\\qquad\qquad\quad\, pairs in the paper,
absurdly high. But measures like that are\\\qquad\qquad\quad\, not confidence-inspiring, so on balance, low.}

%%%% The Proceedings Chair will fill in the following
%%%% two fields.
\papernum{NN}
\papertitle{UNKNOWN PAPER TITLE}

@@

%%% Replace the following text with your review.
Masterful job of optimizing an ``objective'' measure by gaming the data.

This is a poster-child for the application of Goodhart’s Law and the vacuousness of so-called
``objective'' rankings that blindly count stuff – like h-index and impact factors
